Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
on training schema

\subsection{Training Schemes}

\subsection{State of the Art}

>>>>

\subsection{Learning Schemes}
Multi-agent learning can be categorized based on the training scheme and the information accessibility for agents. 
Two prominent paradigms are centralized training with decentralized execution (CTDE) and decentralized training with decentralized execution (DTDE).

\paragraph{Centralized Training with Decentralized Execution (CTDE)}
In CTDE, a central learner trains all agents, 
but execution of the learned policy is decentralized. 
This process typically involves two phases:
\begin{itemize}
    \item \textbf{Offline training:} agents interact with a simulator or environment, 
    gathering experience data used to update the central learner's policy.
    \item \textbf{Online execution:} agents deploy the learned policy in the environment without further learning.
\end{itemize}
This approach offers several benefits.  
Leveraging a centralized dataset allows for efficient learning, 
potentially exploiting global information, 
which is crucial in cooperative scenarios requiring coordinated actions. 
Furthermore, decentralized execution allows agents to act independently after training.
%
However, CTDE has limitations. 
Scalability can become problematic with a large number of agents. 
The reliance on a central learner hinders adaptation to dynamic environments or tasks during runtime.
\sloppy
\paragraph{Decentralized Training with Decentralized Execution (DTDE)}
DTDE eliminates the central learner; each agent learns independently. 
Inter-agent cooperation and communication can be incorporated during both training and execution. 
Unlike CTDE, training and execution phases are not necessarily separate. 
Simultaneous learning and execution allow for adaptation to changing environments or tasks at runtime.
%
Key advantages of DTDE include scalability with the number of agents and adaptability to dynamic environments.
%
However, DTDE faces challenges. 
Convergence time is often longer compared to centralized training. 
The lack of central coordination can lead to instability and difficulties in differentiating agents and their environmental interactions. 
Online learning in DTDE can introduce non-stationarity if agents do not account for other agents' evolving policies during training, 
as the environment effectively changes from each agent's perspective.
\subsection{State of the Art}
